---
title: "Missing Data"
author: "Murray Cadzow"
output: html_notebook
---

```{r}
# install.packages("devtools")

# the development version from GitHub

# devtools::install_github("hadley/tidyverse")
library(tidyverse)
```

# Summarising Data

## skimr

https://github.com/ropenscilabs/skimr

```{r}
# install.packages("devtools")
# devtools::install_github("hadley/colformat")
# devtools::install_github("ropenscilabs/skimr")
library(skimr)
```


load some data sets
```{r}
data("iris")
data("airquality")
```

The skim() function prints out a summary of your data. The summary varies based on the data type.

```{r}
skim(iris)
```

The summary is very similar to the summary() function but also includes information about the total number, number missing and number of complete entries.

Produces separate output for the different data types

And can also produce a long format
```{r}
skim(iris) %>% View()
```

You can filter the long format to pull out a particular statistic
```{r}
skim(iris) %>% filter(stat == 'hist')
```


```{r}
skim(airquality)
```

To get a summary of a single variable use skim_v()
```{r}
skim_v(iris$Sepal.Length)
```




# Missing Data

## Visdat

https://github.com/njtierney/visdat

Visdat is a package developed to allow you to visually check that R has loaded your data as you expected and to also get a sense of how complete your data is

```{r}
# devtools::install_github("njtierney/visdat")
library(visdat)
```

```{r}
vis_dat(iris)
```


```{r}
vis_dat(typical_data)
```

The default behaviour is to group similar datatypes

making sort_type = FALSE means that the data frame columns are returned in the original order

```{r}
vis_dat(typical_data, sort_type = FALSE)
```

vis_miss() can be used to visualise the the completeness of the data

```{r}
vis_miss(airquality)
```

And you can also use it to get a sense of the scale of the problem

```{r}
vis_miss(airquality,cluster = TRUE)
```

## Narnia

https://github.com/njtierney/narnia

Narnia is a package developed to enable the plotting of missing data

By default ggplot2 doesn't allow the plotting of NAs and will automatically filter them out

```{r}
ggplot(data = airquality,
       aes(x = Ozone,
           y = Solar.R)) +
  geom_point()
```

Narnia adds new geoms to ggplot that enable the plotting of NA data.

The geom_missing_point will take your missing data and assign it a value that is outside of 

```{r}
#devtools::install_github("njtierney/narnia")
library(narnia)

ggplot(data = airquality,
       aes(x = Ozone,
           y = Solar.R)) +
  geom_missing_point()
```

in the background it uses the shadow_shift() function

```{r}
airquality %>% mutate(Ozone_shift = shadow_shift(Ozone))
```


Shadow matrix
```{r}
as_shadow(airquality)
```



```{r}
aq_shadow <- bind_shadow(airquality)

aq_shadow
```



```{r}
p1 <- ggplot(data = aq_shadow,
       aes(x = Temp)) + 
  geom_histogram() + 
  facet_wrap(~Ozone_NA,
             ncol = 1)

p2 <- ggplot(data = aq_shadow,
       aes(x = Temp,
           colour = Ozone_NA)) + 
  geom_density() 

gridExtra::grid.arrange(p1, p2, ncol = 2)
```

Offers numerical summaries too

```{r}
# Proportion of variables that contain any missing values
miss_var_pct(airquality)

 # Proportion of cases that contain any missing values
miss_case_pct(airquality)

# Proportion elements in dataset that contains missing values
miss_df_pct(airquality)

```

You can also get the number and percent missing on a column (var) and row (case) basis with miss_var_summary() and miss_case_summary()
```{r}
miss_var_summary(airquality)
miss_case_summary(airquality)
```

plotting missing NA summaries

```{r}
gg_missing_var(airquality)
```

```{r}
gg_missing_case(airquality)
```

Visually identify any column that contains missing values

grey = missing

```{r}
gg_missing_which(airquality)
```

