---
title: "kable tables"
author: "Murray Cadzow"
date: "8 August 2017"
output:
  html_document:
    toc: yes
    toc_float: yes
  pdf_document:
    toc: yes
---

```{r setup, include=FALSE}
library(knitr)
library(kableExtra)
library(tidyverse)
knitr::opts_chunk$set(echo = TRUE)

iris_dat <- datasets::iris
iris_head <- head(iris_dat)
```



kable comes with knitr

can output table in html, latex, markdown, pandoc


some good reference material

- https://rdrr.io/cran/knitr/man/kable.html
- https://cran.r-project.org/web/packages/kableExtra/vignettes/awesome_table_in_html.html



## Plain kable

```{r, results='asis'}
kable(iris_head)
```

rounding
```{r}
kable(iris_head, digits = 0, caption = 'my rounded table')
```

### add row.names

by default kable won't display row names if they are set to NULL or are 1:NROW()


```{r}
rownames(iris_head) <- paste0("row", 1:NROW(iris_head))
iris_head
```


### alignment

```{r}
kable(iris_head, align = 'c', caption = 'my aligned table')
```

### remove row names and change col names
```{r}
kable(iris_head, align = 'rrrrc', row.names = FALSE, col.names = c('col1','col2','col3','col4','col5'))
```


## kableExtra


By default if you don't specify the output format for kable then pandoc takes care of this, however, pandoc can't handle complex tables so we need to specifiy the format of the tables. We can either do this with

```{r, eval = FALSE}
options(knitr.table.format = "html") 
```


or I have made a little function that finds out the current document type we're making and 

```{r}
get_kable_format <- function(){
  # find out the current document type, if pdf set format as latex, otherwise return html
  doc_type <- rmarkdown::all_output_formats(knitr::current_input())[1]
  if(doc_type == 'pdf_document'){
    return('latex')
  } else {
      return('html')
    }
}


options(knitr.table.format = get_kable_format()) 
## If you don't define format here, you'll need put `format = "html"` in every kable function.
```



### apply some styling

defaults

```{r}
kable(iris_head) %>% 
  kable_styling()
```


striped gives a striped appearance and hover highlights on mouseover

```{r}
kable(iris_head) %>% 
  kable_styling(bootstrap_options = c("striped", "hover"))
```


### Position and width

```{r}
kable(iris_head) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```


### Grouping rows and columns

```{r}
kable(iris_head) %>% 
  kable_styling(bootstrap_options = c("striped")) %>% 
  add_header_above(c(" " = 1, "Sepal" = 2, "Petal" = 2, " " = 1)) %>% 
  add_header_above(c(" " = 1, "Another Group" = 4, " " = 1)) %>% 
  group_rows("Group1", 1, 3) %>% 
  group_rows("Group2", 4, 6)
```

### Collapse rows



```{r}

kable(iris_head, align = "c", row.names = FALSE) %>%
  kable_styling(full_width = F) %>%
  column_spec(1, bold=T) %>%
  collapse_rows(columns = 5)
```



